The Suburbanisation of Poverty in Scotland’s Cities: Urban Regeneration or

### 2016-10-28 markdown/draft_as_notebook.Rmd
start on presentation; create notebook doc

---
title: 'The Suburbanisation of Poverty in Scotland’s Cities: Urban Regeneration or
  Social Cleansing?'
author: "Jon Minton & Nick Bailey"
date: "31 August 2016"
output: html_document
---

@@

```{r show_id_map, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
simd_2011_reweighted %>% 
  dplyr::select(dz_2011, year, pop_incomedeprived, pop_total) %>%
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  mutate(prop_id = ifelse(prop_id > 0.5, 0.5, prop_id)) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  append_data(
    shp = dz_2011, data = . ,
    key.shp = "DataZone", key.data = "dz_2011", ignore.na = T
  ) %>% 
  tm_shape(.) + 
  tm_facets(ncol = 3) + 
  tm_fill(
    col = c("2004", "2006", "2009", "2012", "2016"), 
    palette = brewer.pal(10, "Spectral"), 
    breaks = seq(0, 0.5, by = 0.05), showNA = F
    ) -> id_chor_dz2011

@@

```{r show_id_map_glasgow, echo = F, eval = T, message = FALSE, warning = FALSE}

@@

```{r show_id_map_edinburgh, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}

@@

```{r show_id_map_dundee, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}

@@

```{r show_id_map_aberdeen, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}

@@

```{r show_temporal_dep, echo = FALSE, warning = FALSE, EVAL = TRUE}
simd_2011_reweighted %>% 
  filter(year %in% c(2004, 2016)) %>% 
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  rename(prop_id_2004 = `2004`, prop_id_2016 = `2016`) %>% 
  ggplot(., aes(x = prop_id_2004, y = prop_id_2016)) + 
  geom_point(alpha = 0.1) + 
  geom_abline(colour = "blue", slope = 1, intercept = 0) + 
  stat_smooth(colour = "red", linetype = "dashed") + 
  labs(
    x = "ID prop, 2004", y = "ID prop, 2016",
    title = "2016 against 2004"
       ) -> s_04_16

@@

```{r id_prop_by_year, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
  simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>%
    filter(distance_to_centre < 15000) %>% 
    group_by(nearest_centre, year) %>% 
    summarise(pop_total = sum(pop_total), pop_incomedeprived = sum(pop_incomedeprived)) %>% 
    mutate(prop_id = pop_incomedeprived / pop_total) %>% 
    mutate(prop_id = 100 * round(prop_id, 3)) %>% 
    dplyr::select(City = nearest_centre, prop_id, Year = year) %>% 
    spread(Year, prop_id) %>% 
    ungroup() %>% 
    arrange(`2004`) %>% 
    kable(., format = "markdown", caption = "Income deprived % by City and Year")

@@

```{r plot_change_rci, eval = TRUE, echo = FALSE, warning = FALSE}
# Do RCI graph

@@

```{r plot_change_d, eval = TRUE, echo = FALSE, warning = FALSE}
# Do D graph

@@

```{r show_change_in_id, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
decent_plot_for_city <- function(this_city){
  simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
    filter(nearest_centre == this_city) %>%
    distinct() %>% 
    mutate(prop_id = pop_incomedeprived / pop_total) %>% 
    dplyr::select(dz_2011, distance_to_centre, year, prop_id) %>% 
    mutate(distance_to_centre = distance_to_centre / 1000) %>%
    filter(distance_to_centre < 30) %>% 
    spread(year, prop_id) %>% 
    mutate(change = `2016` - `2004`) %>% 
    ggplot(., aes(x = distance_to_centre, y = change)) + 
    geom_point( alpha = 0.01) + 
    scale_x_continuous(limits = c(0.5, 30), breaks = c(0.5, 1, 2, 5, 10, 20)) + 
    scale_y_continuous(limits = c(-0.25, 0.25) ) +
    stat_smooth() + 
    geom_hline(aes(yintercept = 0), linetype = "dashed") + 
    geom_vline(aes(xintercept = 1e+0)) + 
    geom_vline(aes(xintercept = 1.2e+1)) + 
    labs(x = "Distance to centre (km)", y = "Change in ID",
         title = this_city)
}

@@

```{r plot_changeidpop, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
idpopchange_plot_for_city <- function(this_city){
  simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
    filter(nearest_centre == this_city) %>%
    distinct() %>% 
    dplyr::select(dz_2011, distance_to_centre, year, pop_incomedeprived) %>% 
    mutate(distance_to_centre = distance_to_centre / 1000) %>% 
    spread(year, pop_incomedeprived) %>% 
    mutate(change = (`2016` / `2004`) - 1) %>% 
    ggplot(., aes(x = distance_to_centre, y = change)) + 
    geom_point( alpha = 0.01) + 
    scale_x_log10(limits = c(0.5, 50), breaks = c(0.5, 1, 2, 5, 10, 20, 50)) + 
    scale_y_continuous(limits = c(-.5, .5)) +    
    stat_smooth() + 
    geom_vline(aes(xintercept = 1e+0)) + 
    geom_vline(aes(xintercept = 1.2e+1)) +
    geom_hline(aes(yintercept = 0), linetype = "dashed") + 
    labs(x = "Distance to centre (km)", y = "Change in ID pop",
         title = this_city)
}

@@

```{r plot_changetotalpop, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
totalpopchange_plot_for_city <- function(this_city){
  simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
    filter(nearest_centre == this_city) %>%
    distinct() %>% 
    dplyr::select(dz_2011, distance_to_centre, year, pop_total) %>% 
    mutate(distance_to_centre = distance_to_centre / 1000) %>% 
    spread(year, pop_total) %>% 
    mutate(change = (`2016` / `2004`) - 1) %>% 
    ggplot(., aes(x = distance_to_centre, y = change)) + 
    geom_point( alpha = 0.01) + 
    scale_x_log10(limits = c(0.5, 50), breaks = c(0.5, 1, 2, 5, 10, 20, 50)) + 
    scale_y_continuous(limits = c(-.5, .5)) +    
    stat_smooth() + 
    geom_vline(aes(xintercept = 1e+0)) + 
    geom_vline(aes(xintercept = 1.2e+1)) +
    geom_hline(aes(yintercept = 0), linetype = "dashed") + 
    labs(x = "Distance to centre (km)", y = "Change in total pop",
         title = this_city)
}

>>>>

---
title: 'The Suburbanisation of Poverty in Scotland’s Cities: Urban Regeneration or
  Social Cleansing?'
author: "Jon Minton & Nick Bailey"
date: "31 August 2016"
output: html_notebook
---

@@

```{r show_id_map, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, dpi = 300, fig.width = 15}
simd_2011_reweighted %>% 
  dplyr::select(dz_2011, year, pop_incomedeprived, pop_total) %>%
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  mutate(prop_id = ifelse(prop_id > 0.5, 0.5, prop_id)) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  append_data(
    shp = dz_2011, data = . ,
    key.shp = "DataZone", key.data = "dz_2011", ignore.na = T
  ) %>% 
  tm_shape(.) + 
  tm_facets(ncol = 3) + 
  tm_fill(
    col = c("2004", "2006", "2009", "2012", "2016"), 
    palette = brewer.pal(10, "Spectral"), 
    breaks = seq(0, 0.5, by = 0.05), showNA = F
    ) -> id_chor_dz2011

@@

```{r show_id_map_glasgow, echo = F, eval = T, message = FALSE, warning = FALSE, dpi = 300, fig.width = 15}

@@

```{r show_id_map_edinburgh, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, dpi = 300, fig.width = 15}

@@

```{r show_id_map_dundee, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, dpi = 300, fig.width = 15}

@@

```{r show_id_map_aberdeen, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, dpi = 300, fig.width = 15}

@@

```{r show_temporal_dep, echo = FALSE, warning = FALSE, EVAL = TRUE, dpi = 300, fig.width = 15}
simd_2011_reweighted %>% 
  filter(year %in% c(2004, 2016)) %>% 
  mutate(prop_id = pop_incomedeprived / pop_total) %>% 
  dplyr::select(dz_2011, year, prop_id) %>% 
  spread(year, prop_id) %>% 
  rename(prop_id_2004 = `2004`, prop_id_2016 = `2016`) %>% 
  ggplot(., aes(x = prop_id_2004, y = prop_id_2016)) + 
  geom_point(alpha = 0.1) + 
  geom_abline(colour = "blue", slope = 1, intercept = 0) + 
  stat_smooth(colour = "red", linetype = "dashed") + 
  labs(
    x = "ID prop, 2004", y = "ID prop, 2016",
    title = "2016 against 2004"
       ) -> s_04_16

@@

```{r id_prop_by_year, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
  simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>%
    filter(distance_to_centre < 15000) %>% 
    group_by(nearest_centre, year) %>% 
    summarise(pop_total = sum(pop_total), pop_incomedeprived = sum(pop_incomedeprived)) %>% 
    mutate(prop_id = pop_incomedeprived / pop_total) %>% 
    mutate(prop_id = 100 * round(prop_id, 3)) %>% 
    dplyr::select(City = nearest_centre, prop_id, Year = year) %>% 
    spread(Year, prop_id) %>% 
    ungroup() %>% 
    arrange(`2004`) %>% 
    kable(., format = "markdown", caption = "Income deprived % by City and Year", )

@@

```{r plot_change_rci, eval = TRUE, echo = FALSE, warning = FALSE, dpi = 300}
# Do RCI graph

@@

```{r plot_change_d, eval = TRUE, echo = FALSE, warning = FALSE, dpi = 300}
# Do D graph

@@

```{r show_change_in_id, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE, dpi = 300, fig.width = 20, fig.height = 15}
decent_plot_for_city <- function(this_city){
  simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
    filter(nearest_centre == this_city) %>%
    distinct() %>% 
    mutate(prop_id = pop_incomedeprived / pop_total) %>% 
    dplyr::select(dz_2011, distance_to_centre, year, prop_id) %>% 
    mutate(distance_to_centre = distance_to_centre / 1000) %>%
    filter(distance_to_centre < 30) %>% 
    spread(year, prop_id) %>% 
    mutate(change = `2016` - `2004`) %>% 
    ggplot(., aes(x = distance_to_centre, y = change)) + 
    geom_point( alpha = 0.01) + 
    scale_x_continuous(limits = c(0.5, 30), breaks = c(0.5, 1, 2, 5, 10, 20)) + 
    scale_y_continuous(limits = c(-0.25, 0.25) ) +
    stat_smooth() + 
    geom_hline(aes(yintercept = 0), linetype = "dashed") + 
    geom_vline(aes(xintercept = 1e+0)) + 
    geom_vline(aes(xintercept = 1.2e+1)) + 
    labs(x = "Distance to centre (km)", y = "Change in ID",
         title = this_city)
}

@@

```{r plot_changeidpop, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE,dpi = 300, fig.width = 20, fig.height = 15}
idpopchange_plot_for_city <- function(this_city){
  simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
    filter(nearest_centre == this_city) %>%
    distinct() %>% 
    dplyr::select(dz_2011, distance_to_centre, year, pop_incomedeprived) %>% 
    mutate(distance_to_centre = distance_to_centre / 1000) %>% 
    spread(year, pop_incomedeprived) %>% 
    mutate(change = (`2016` / `2004`) - 1) %>% 
    ggplot(., aes(x = distance_to_centre, y = change)) + 
    geom_point( alpha = 0.01) + 
    scale_x_log10(limits = c(0.5, 50), breaks = c(0.5, 1, 2, 5, 10, 20, 50)) + 
    scale_y_continuous(limits = c(-.5, .5)) +    
    stat_smooth() + 
    geom_vline(aes(xintercept = 1e+0)) + 
    geom_vline(aes(xintercept = 1.2e+1)) +
    geom_hline(aes(yintercept = 0), linetype = "dashed") + 
    labs(x = "Distance to centre (km)", y = "Change in ID pop",
         title = this_city)
}

@@

```{r plot_changetotalpop, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE, dpi = 300, fig.width = 20, fig.height = 15}
totalpopchange_plot_for_city <- function(this_city){
  simd_2011_reweighted  %>% 
    ungroup() %>%  
    left_join(centre_distance, by = c("dz_2011" = "datazone")) %>% 
    filter(nearest_centre == this_city) %>%
    distinct() %>% 
    dplyr::select(dz_2011, distance_to_centre, year, pop_total) %>% 
    mutate(distance_to_centre = distance_to_centre / 1000) %>% 
    spread(year, pop_total) %>% 
    mutate(change = (`2016` / `2004`) - 1) %>% 
    ggplot(., aes(x = distance_to_centre, y = change)) + 
    geom_point( alpha = 0.01) + 
    scale_x_log10(limits = c(0.5, 50), breaks = c(0.5, 1, 2, 5, 10, 20, 50)) + 
    scale_y_continuous(limits = c(-.5, .5)) +    
    stat_smooth() + 
    geom_vline(aes(xintercept = 1e+0)) + 
    geom_vline(aes(xintercept = 1.2e+1)) +
    geom_hline(aes(yintercept = 0), linetype = "dashed") + 
    labs(x = "Distance to centre (km)", y = "Change in total pop",
         title = this_city)
}
